\section*{Note from the Authors}
This game is a non-profit fan production intended to turn the complex and storied Elder Scrolls setting into a playable pencil-and-paper RPG. Elder Scrolls and all products under its name are owned by Bethesda Softworks and Bethesda Game Studios. We do not intend to profit off of this in any way. Please support the creators by buying their games and products.\\~\\
By participating in our game as a playtester, you agree to the following terms:

\begin{enumerate}
	\item You will not sell any portion of this game under any circumstances.
	\item You acknowledge that any rules and game mechanics may be subject to change by the authors in the service of better gameplay.
	\item You agree to help foster an inclusive, respectful atmosphere for all players. While we trust you all to do this, it bears repeating.
\end{enumerate}
In return, we promise the following to you:

\begin{enumerate}
	\item Our top priority is and always will be the creation of a satisfying gameplay experience.
	\item We will attempt to implement game changes in an unobtrusive way whenever possible.
	\item We will treat players with respect both out-of-character and in the way we create our narrative (even if player characters may not be respected).
	\item We encourage you to voice your concerns in any way you feel comfortable and will listen to your feedback.
\end{enumerate}
We hope you enjoy our game!
\newpage

\section*{About the Game}

Elder Scrolls is a vast, intricate fantasy setting. Attempting to compile relevant information here would be an effort in futility without a specific time and place in mind, and these rules are easily applicable to any setting throughout much of the Second, Third and early Fourth Eras. The game is largely based on the game mechanics of Elder Scrolls IV: Oblivion and Elder Scrolls III: Morrowind. Some modification would be necessary to make it function more like Elder Scrolls V and set it later in the Fourth Era, but it is possible if you were inclined to do so. For now, please refer to online sources for lore information. In particular, the Unofficial Elder Scrolls Project is a comprehensive and accurate source for information about all things Elder Scrolls. Much of the lore material here is taken from UESP --- a benefit of this being a not-for-profit fan creation.
